### 2020-03-30 Writing/disparity_review.tex
Updated vera's affiliation

Thomas Guillerme$^{1,17,*, +}$,
Natalie Cooper$^{2, +}$,
Stephen L. Brusatte$^{3}$,
Katie E. Davis$^{4}$,
Andrew L. Jackson$^{5}$,
Sylvain Gerber$^{6}$,
Anjali Goswami$^{2}$,
Kevin Healy$^{7}$,
Melanie J. Hopkins$^{8}$,
Marc E. H. Jones$^{9}$,
Graeme T. Lloyd$^{10}$,
Joseph E. O'Reilly$^{11}$, %was 17 - 11 forward + 1
Abi Pate$^{12}$,
Mark N. Puttick$^{13}$,
Emily Rayfield$^{12}$,
Erin E. Saupe$^{14}$,
Emma Sherratt$^{15}$,
Graham J. Slater$^{16}$,
Vera Weisbecker$^{1}$,
Gavin H. Thomas$^{17}$
and Philip C. J. Donoghue$^{12}$

\noindent{
$^{1}$ School of Biological Sciences, University of Queensland, St. Lucia,
Queensland, Australia;
$^{2}$ Department of Life Sciences, Natural History Museum, London, Cromwell
Road, London, SW7 5BD, UK;
$^{3}$ School of GeoSciences, University of Edinburgh, Grant Institute,
Edinburgh EH9 3FE, UK;
$^{4}$ Leverhulme Centre for Anthropocene Biodiversity, Department of
Biology, University of York, YO10 5DD, UK;
$^{5}$ Department of Zoology, School of Natural Sciences, Trinity College
Dublin, Ireland;
$^{6}$ Institut de Syst\'{e}matique, \'{E}volution, Biodiversit\'{e} (ISYEB), Mus\'{e}um national d'Histoire naturelle, CNRS, Sorbonne Universit\'{e}, EPHE, Universit\'{e} des Antilles, 57 rue Cuvier CP39, 75005 Paris, France;
$^{7}$ Ryan Institute, School of Natural Sciences, National University of
Ireland Galway, Ireland;
$^{8}$ Division of Paleontology (Invertebrates), American Museum of Natural
History, New York, USA;
$^{9}$ Department of Cell and Developmental Biology, University College
London, London, UK;
$^{10}$ School of Earth and Environment, University of Leeds, Leeds LS2 9JT,
UK;
$^{11}$ MRC Institute of Genetic and Molecular Medicine, University of Edinburgh, UK;
$^{12}$ School of Earth Sciences, University of Bristol, Life Sciences
Building, Tyndall Avenue, Bristol BS8 1TQ, UK;
$^{13}$ Milner Centre for Evolution, University of Bath, BA2 7AY UK;
$^{14}$ Department of Earth Sciences, University of Oxford, S Parks Road,
Oxford OX1 3AN, UK;
$^{15}$ School of Biological Sciences, The University of Adelaide, Adelaide,
South Australia 5005, Australia.
$^{16}$ Department of the Geophysical Sciences, University of Chicago,
Chicago, Illinois 60637;
$^{17}$ Department of Animal and Plant Sciences, The University of Sheffield,
Sheffield S10 2TN, UK;\\
$^{+}$ These authors contributed equally to the manuscript; $^{*}$ Corresponding
author: guillert@tcd.ie}

>>>>

Thomas Guillerme$^{1,18,*, +}$,
Natalie Cooper$^{2, +}$,
Stephen L. Brusatte$^{3}$,
Katie E. Davis$^{4}$,
Andrew L. Jackson$^{5}$,
Sylvain Gerber$^{6}$,
Anjali Goswami$^{2}$,
Kevin Healy$^{7}$,
Melanie J. Hopkins$^{8}$,
Marc E. H. Jones$^{9}$,
Graeme T. Lloyd$^{10}$,
Joseph E. O'Reilly$^{11}$, %was 17 - 11 forward + 1
Abi Pate$^{12}$,
Mark N. Puttick$^{13}$,
Emily Rayfield$^{12}$,
Erin E. Saupe$^{14}$,
Emma Sherratt$^{15}$,
Graham J. Slater$^{16}$,
Vera Weisbecker$^{1,17}$,
Gavin H. Thomas$^{18}$
and Philip C. J. Donoghue$^{12}$

\noindent{
$^{1}$ School of Biological Sciences, University of Queensland, St. Lucia,
Queensland, Australia;
$^{2}$ Department of Life Sciences, Natural History Museum, London, Cromwell
Road, London, SW7 5BD, UK;
$^{3}$ School of GeoSciences, University of Edinburgh, Grant Institute,
Edinburgh EH9 3FE, UK;
$^{4}$ Leverhulme Centre for Anthropocene Biodiversity, Department of
Biology, University of York, YO10 5DD, UK;
$^{5}$ Department of Zoology, School of Natural Sciences, Trinity College
Dublin, Ireland;
$^{6}$ Institut de Syst\'{e}matique, \'{E}volution, Biodiversit\'{e} (ISYEB), Mus\'{e}um national d'Histoire naturelle, CNRS, Sorbonne Universit\'{e}, EPHE, Universit\'{e} des Antilles, 57 rue Cuvier CP39, 75005 Paris, France;
$^{7}$ Ryan Institute, School of Natural Sciences, National University of
Ireland Galway, Ireland;
$^{8}$ Division of Paleontology (Invertebrates), American Museum of Natural
History, New York, USA;
$^{9}$ Department of Cell and Developmental Biology, University College
London, London, UK;
$^{10}$ School of Earth and Environment, University of Leeds, Leeds LS2 9JT,
UK;
$^{11}$ MRC Institute of Genetic and Molecular Medicine, University of Edinburgh, UK;
$^{12}$ School of Earth Sciences, University of Bristol, Life Sciences
Building, Tyndall Avenue, Bristol BS8 1TQ, UK;
$^{13}$ Milner Centre for Evolution, University of Bath, BA2 7AY UK;
$^{14}$ Department of Earth Sciences, University of Oxford, S Parks Road,
Oxford OX1 3AN, UK;
$^{15}$ School of Biological Sciences, The University of Adelaide, Adelaide,
South Australia 5005, Australia.
$^{16}$ Department of the Geophysical Sciences, University of Chicago,
Chicago, Illinois 60637;
$^{18}$ College of Science and Engineering, Flinders University,
Adelaide SA5042, Australia;\\
$^{18}$ Department of Animal and Plant Sciences, The University of Sheffield,
Sheffield S10 2TN, UK;\\
$^{+}$ These authors contributed equally to the manuscript; $^{*}$ Corresponding
author: guillert@tcd.ie}
